GSS Education Analysis (Working Title)

### 2023-03-15 outputs/paper/paper.qmd
add to results section

@@

From looking at @fig-3,

According to **Figure 3**, the two highest levels of education still make up a significant portion of the \"More or Less Satisfied\" and the \"Not Satisfied at All'' groups.

>>>>

#### Ordering Financial Satisfaction####

cleaned_gss_2021$satfin <- 
  factor(cleaned_gss_2021$satfin, 
         levels = c("Pretty Well Satisfied", "More or Less Satisfied", "Not Satisfied at All"))
```

@@

@fig-3 demonstrates that most respondents are "more or less satisfied" or higher when discussing their degree of financial satisfaction. Importantly, we can see that those with higher levels of education have higher rates within their group of being "pretty well satisfied" with their financial standing, than those with lower levels of education. Additionally, we can see that those with associate or junior college level education are the most balanced in all levels of financial satisfaction, alluding to the idea that specific type of degree is influential in how respondents may respond.
